%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Grants and Scholarships}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%%---------------------------------------------------------
  \cventry
    {Predoctoral researcher} % Job title
    {YEI Grant Predoctoral Researchers 2016} % Organization
    {Madrid, Spain} % Location
    {Apr. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Community of Madrid PEJD-2016/TIC-2633}
      \end{cvitems}
    }

  \cventry
    {Predoctoral researcher} % Job title
    {Research Stay at Computational Sciences Department. Monterrey Institute of Technology and Higher Education (ITESM)} % Organization
    {Puebla, Mexico} % Location
    {Aug. 2016 - Apr. 2017} % Date(s)
    {
    \begin{cvitems}
     \item {Tutor: Prof. Alberto Oliart}
     \item {\textit{Becas Iberoamérica Jóvenes Profesores e Investigadores 2016} International Research Grant}
     \item {Project: Neural model of electrical discharge in fish electricians of the species \textit{Gnathonemus petersii}.}
    \end{cvitems}
    }

  \cventry
    {M.S.} % Job title
    {Grant of the Department of Computer Engineering EPS-UAM (2015) for the start of doctoral studies.} % Organization
    {Madrid, Spain} % Location
    {Oct. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Doctorate in Computer Engineering and Telecommunications (RD2011) at Biological Neurocomputation Group (GNB).}
      \end{cvitems}
    }

  \cventry
    {B.E.} % Job title
    {Grant of the Department of Computer Engineering EPS-UAM (2013) for Master's Degree Enrollment.} % Organization
    {Madrid, Spain} % Location
    {Oct. 2013 - Oct. 2014} % Date(s)
    {
     \begin{cvitems}
     	\item (Master's program in Research and Innovation in Information and Communications Technologies (I2-TIC) at Biological Neurocomputation Group (GNB)..)
     \end{cvitems}
    }

\end{cventries}